A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-22 6_validation.tex
explain statistics (extra change)
remove wrapfigure because that is already explained in the appendix (extra change)

\revise{}
{
\subsection{Computational results}\label{sec_computational_results}
} % tew
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
\begin{wrapfigure}{r}{.3\columnwidth}
\centering
\includegraphics[width=.25\columnwidth]{sources-validation-visualization-principle-rounded-excluded-single.pdf}
\caption{
Extrusion segments coverage.
The hole at the end will be filled by the next extrusion segment.
}
\label{segment_visualization_simple}
\end{wrapfigure}
We construct the over- and underfill area by comparing the shapes covered by each extrusion move (\cref{segment_visualization_simple}) with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.

We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in see \cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.

>>>>

\revise{}
{
\subsection{Computational results}\label{sec_computational_results}
} % tew
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
%
%
We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in see \cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.
